### 2015-11-02 CVPR16/Source/experiments.tex
Added visualizations for the RAS algorithm.

%\begin{table}
%  \centering
%  \begin{tabular}{lccc}
%    \toprule
%    Algorithm & All & Unoccluded cars & Occluded cars \\
%    \midrule
%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
%    \bottomrule
%  \end{tabular}
%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
%\end{table}
\begin{figure*}
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}
  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
  \label{fig:assoc-occ-results}
\end{figure*}

@@

\newpage
\begin{table*}
  \begin{tabular}{ccc}
    & Assignments & Error in assignment\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{05pt} Brox and Malik} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=0.48\textwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
\end{table*}

>>>>

%\begin{table}
%  \centering
%  \begin{tabular}{lccc}
%    \toprule
%    Algorithm & All & Unoccluded cars & Occluded cars \\
%    \midrule
%    bounding box only                         & $0.18\pm0.01$          & $\color{red}0.04\pm0.003$  & $0.41\pm0.04$\\
%    Using $\assocP{}$                         & $0.18\pm0.01$          & $0.05\pm0.003$           & $0.39\pm0.04$ \\
%    Using $P^{(ij)}_{\text{assoc by reproj}}$ & $0.18\pm0.01$          & $0.06\pm0.003$           & $0.39\pm0.04$\\
%    Using $P^{(ij)}_{\text{assoc}}$           & $\color{red}0.17\pm0.01$ & $0.05\pm0.003$           & $\color{red}0.38\pm0.04$\\
%    \bottomrule
%  \end{tabular}
%  \caption{Association Experiment results. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. }
%\end{table}
\begin{figure*}
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_static_and_dynamic.pdf}\\
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}\\
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_50.pdf}\\
  \includegraphics[width=\textwidth]{results/plotErrorBarEvalAssocCoeffAllSequence_occ_50.pdf}
  \caption{From top: (1)Association Experiment results on all points. %} \label{fig:assoc-results}
    (2) Association Experiment results on occluded points. %} \label{fig:assoc-occ-results}
    (3) Association Experiment results on dynamic points. %} \label{fig:assoc-dynamic-results}
    (4) Association Experiment results on dynamic  and occluded points. The error is in terms of average fraction of foreground points incorrectly associated to objects per sequence. } \label{fig:assoc-occ-results}
\end{figure*}

@@

\newpage
\newlength{\tblimgwidth}
\setlength{\tblimgwidth}{0.40\textwidth}
\begin{table*}
  \centering
  \begin{tabular}{ccc}
    & Assignments & Error in assignment\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0009_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} BBox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_bbox2D_model_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Brox} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_BroxAndMalik2010_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} RAS} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_RAS_correct_incorrect-small.png}\\
    \rotatebox{90}{\hspace{2em} Ours} & \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks-small.png} &%
    \includegraphics[width=\tblimgwidth]{results/0013_0000000060_point_assign_contPtTracks_correct_incorrect-small.png}
  \end{tabular}
  \caption{Qualitative results for association experiment. The left column
  shows the point tracks assignment to appropriate track. Each color represents
a different track to which the point is associated to. Right column shows the
probablistic error in association: red is low error and blue is high error.
Note that our method changes smoothly at the boundary of the objects with
intermediate probabilities, while the baseline methods have only 0-1 error.} 
\end{table*}

### 2015-11-02 CVPR16/Source/occlusion.tex
Added visualizations for the RAS algorithm.

\paragraph{Occupancy model for traffic participants}
Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy. We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque, while regions more likely to be free space are more transparent. Based on this intuition, we model objects as translucent 3D ellipsoids whos opacity is maximum at the center and falls off towards the edges. In particular, we model the occupancy at location $\bx$ corresponding to a traffic participant $i$ centered at $\pos{i}{t}$ as:
\begin{align}
  f_{\text{occ}}(\bx) = \cL(\bx; \pos{i}{t}, \bSigma_i)
\end{align}
where $\cL(\cdot)$ is the logistic function given by
\begin{align}
  L(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
\end{align}
with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma(\bx-\bp)$ being the Mahalanobis distance. We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center. The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the traffic participant. Please refer to the Chapter~\ref{sec:appendix} for computation of $\bSigma$ from object dimensions.

@@

\paragraph{Transmission probability}
Since we are modeling occupancy as transparency, we look towards optics for modeling of translucent objects. A model for transmission of light through a material of thickness $\alpha$, density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
\begin{align}
I(x) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function $\occftot = \sum_i \occf$. Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
%
\begin{align}
  \!\!\!\! P_{\textit{transmission}}(\lambda + d\lambda) = P_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
\end{align}
%
For an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
P^j_{\textit{transmission}}(\lambda) = \prod_{f}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
\label{eq:ptrans-integral}
\end{align}
where $\displaystyle\prod_{f}^{\lambda}$ represents the \emph{product integral} from $f$ to $\lambda$ and $f$ is the position of camera screen which has been taken equivalent to focal length of the camera .\footnote{A product integral is a simple integral in log domain: 
\vspace{-0.2cm}
\begin{equation}
\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
\end{equation}
}

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability:
%
%\newcommand{\Ptrans}{P_{\textit{transmission}}}%
\begin{align}
  \Ptrans^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\nu_i$ the mean depth of object $O_i$. That is,
%
\begin{align}
\cL_u(\bu; \bmu_i, \bGamma_i^{-1}) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}} \\
\cL_{\lambda}(\lambda; \nu_i) &= \frac{1}{1 + e^{-k_d(\lambda - \nu_i)}}
\end{align}
%
We compare the exact and relative formulation of transmission probability in Fig~\ref{fig:compare:exact:approx:ptrans}.

>>>>

\paragraph{Occupancy model for traffic participants}
Intuitively, we consider traffic participants to be regions of 3D space with a high probability of occupancy. We model the uncertainty in occupancy as a translucency function, with regions more likely to be occupied by an object considered more opaque, while regions more likely to be free space are more transparent. Based on this intuition, we model objects as translucent 3D ellipsoids whos opacity is maximum at the center and falls off towards the edges. In particular, we model the occupancy at location $\bx$ corresponding to a traffic participant $i$ centered at $\pos{i}{t}$ as:
\begin{align}
  f_{\text{occ}}(\bx) = \cL(\bx; \pos{i}{t}, \bSigma_i)
\end{align}
where $\cL(\cdot)$ is the logistic function given by
\begin{align}
  L(\bx; \bp, \bSigma) = \frac{1}{1 + e^{-k(1 - d(\mathbf{x},\bp))}},
\end{align}
with $d(\bx, \bp) = (\bx-\bp)^\top\bSigma(\bx-\bp)$ being the Mahalanobis distance. We set $k = 10\ln{49}$ as the value that allows the logistic function $\cL$ to drop to $0.98$ at a distance $d = 0.9$ from the object center. The spread of the ellipsoid, determined by $\bSigma_i$, depends of the dimensions of the traffic participant. Please refer to the supplementary material for computation of $\bSigma_i$ from object dimensions.

@@

\paragraph{Transmission probability}
Since we are modeling occupancy as transparency, we look towards optics for modeling of translucent objects. A model for transmission of light through a material of thickness $\alpha$, density $\rho$ and opacity $\beta$ is given by the Beer-Lambert Law:
\begin{align}
I(x) = I_0 e^{-\beta\rho\alpha}.
\end{align}
%
In our formulation of scene occupancy, both opacity and density at a scene point $\bx_j$ are encapsulated within the total occupancy function $\occftot = \sum_i \occf$. Further, the domain of our ocupancy function $\occftot$ is $[0, 1]$ instead of $[0, \infty)$ for opacity $\beta$. Thus, we replace $e^{-\beta\rho}$ by the transparency function $1 - \occftot$ and consequently, the transmission probability over a small distance $d\lambda$ is given by
%
\begin{align}
  \!\!\!\! P_{\textit{transmission}}(\lambda + d\lambda) = P_{\textit{transmission}}(\lambda) (1-\occftot)^{d\lambda}.
\end{align}
%
For an image point $\bu_j$ to correspond to a 3D point $\bx_j$ at depth $\lambda$ along the backprojected ray $\ray$, the ray must be transmitted through space with the probability
\begin{align}
P^j_{\textit{transmission}}(\lambda) = \prod_{f}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda},
\label{eq:ptrans-integral}
\end{align}
where $\displaystyle\prod_{f}^{\lambda}$ represents the \emph{product integral} from $f$ to $\lambda$ and $f$ is the position of camera screen which has been taken equivalent to focal length of the camera .\footnote{A product integral is a simple integral in log domain: 
\vspace{-0.2cm}
\begin{equation}
\prod_{f}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} = e^{\int_{f}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}. \nonumber
\end{equation}
}

In practice, the integral for transmission probability \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we choose a parameterization in the form of a product of sigmoid functions, which is a reasonable approximation to the behaviour of the transmission probability:
%
\newcommand{\Ptransmission}{P_{\textit{transmission}}}%
\begin{align}
  \Ptransmission^j(\lambda) = \prod_i (1 - \cL_u (\bu; \bmu_i, \bGamma_i^{-1}) \cL_{\lambda}(\lambda; \nu_i)),
\label{eq:evalCumulativePtrans}
\end{align}
%
where $\cL_u(.)$ is sigmoid in image domain, with $\bmu^i_u$ and $\bGamma_i$ representing the elliptical projection of object $O_i$ in the image and $\cL_{\lambda}(.)$ is sigmoid in the depth domain with $\nu_i$ the mean depth of object $O_i$. That is,
%
\begin{align}
\cL_u(\bu; \bmu_i, \bGamma_i^{-1}) &= \frac{1}{1 + e^{-k_u(1 - (\bu - \bmu_i)^\top \bGamma_i^{-1} (\bu - \bmu_i))}} \\
\cL_{\lambda}(\lambda; \nu_i) &= \frac{1}{1 + e^{-k_d(\lambda - \nu_i)}}
\end{align}
%
We compare the exact and relative formulation of transmission probability in
Fig~\ref{fig:compare:exact:approx:ptrans}. Note that the choice of mean depth
of object causes deviation from the exact transmission probability. However,
the computation of ray intersection with ellipsoid is expensive to compute for 
every ray and the shift of transmission probability anywhere through the object 
is a reasonable approximation as the occluded points can only lie outside the
object.

### 2015-11-02 CVPR16/Source/related.tex
Added visualizations for the RAS algorithm.

\section{Related Work}
\label{sec:related}

\paragraph{Occlusion handling in detection}
Several works in object detection consider occlusion by training a detector on visible parts of the object \cite{Gao_etal_2011}. Occlusion reasoning based on 2D image silhouettes is used to improve detection performance in \cite{Hsiao_Herbert_2012}. In contrast, our occlusion reasoning is based on 3D entities. In recent years, object detectors have also considered occlusion reasoning using 3D cues, often learned from a dataset of CAD models \cite{Pepik_etal_2012,Pepik_etal_2013,Xiang_Savarese_2013}. By necessity, such frameworks are often a discrete representation of occlusion behavior, for example, in the form of a collection of occlusion masks derived from object configurations discretized over viewpoint. In constrast to these works, our occlusion modeling is also fully 3D, but allows for a continuous representation. Further, to derive 3D information, we do not use CAD models, rather we derive a probabilistic formulation based on physical insights.

\paragraph{Occlusion handling in tracking}
Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling, however, is much more general in determining the probability of a point in space as belonging to an object. While it can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it can have far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.

>>>>

\section{Related Work}
\paragraph{Occlusion handling in tracking}
Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicits models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling is much more general in determining the probability of a point in space as belonging to an object. While it can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it can have far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.
